---
title: "Testing R Markdown"
author: "Tahmidul Islam"
date: "9/13/2019"
output: html_document

knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GP Regression

First we write the RBF (Gaussian) kernel function.

```{r}
library(kernlab)
# RBF kernel

ker <- function(x, y = 'NULL', l, sigf) {
  rbf <- rbfdot(sigma = 1/l)
  if(y == 'NULL')  return(sigf * kernelMatrix(rbf, x = x))
  else  return(sigf * kernelMatrix(rbf, x = x, y= y))
}

```

Now we make a grid of 10 equally spaced points from 0 to 1 and evaluate the kernel function.
```{r}
x <- seq(0,1, length.out = 10)
round(ker(x = x, l = 1, sigf = 1),2)
```

We are ready to sample from a GP now. We use the covariance matrix produced by the kernel and sample from a zero mean GP.

```{r}
library(mvtnorm)
mu <- rep(0, 10)
sigma <- ker(x = x, l = .5, sigf = 1)
fx <- rmvnorm(1, mean = mu, sigma = sigma)
plot(x, fx, type = 'l', lwd = 2)
```

We can samples from this GP.

```{r}
fx <- rmvnorm(10, mean = mu, sigma = sigma)
plot(x, fx[1,], type = 'l', ylim = c(min(fx), max(fx)), lwd = 2, col = 'grey')
for (i in 1:10) lines(x, fx[i,], lwd = 2, col = 'grey')
```

Now lets try to fit complicated function.

```{r}
gx <- function(x) {sin(10 * x) + cos (20 * x)}
curve(gx,0,1)
```

Now lets create a training dataset by adding white noise to the true function.

```{r}
y <- gx(x) + rnorm(10, 0, 1)
plot(x, y, pch = 16)
```

The marginal likelihood of a GP model is pretty straightforward.$ Y \sim MN(0, K(\cdot, \cdot | \theta) + \sigma^2 I)$ where $(\theta, \sigma^2)$ are treated as hyperparameters. We write a function to compute the log marginal likelihood function.


